Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
minor edits

	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}

>>>>

	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
